---
title: "Decision Analysis for Laser Leveling Application"
author: "Arnaud, Barbacias, Bigerna, Florido, Schönbach"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
subtitle: Creating a decision support model for smale scale farmers in Vietnam using
  the decisionSupport R package by Lüdeling et al.
bibliography: project_packages.bib
editor_options:
  markdown:
    wrap: 72
---

------------------------------------------------------------------------

# Introduction

Water scarcity and the efficient management of water resources have
emerged as major challenges in agricultural development worldwide. With
the increasing impacts of climate change, ensuring sustainable food
production has become a pressing concern. Irrigated rice cultivation
plays a vital role in ensuring global food security, providing a
substantial portion of the world's population with a staple crop
[@bouman_rice_2007]. Rice is a primary dietary staple for billions of
people, particularly in Asia, where it serves as a crucial source of
calories and nutrition [@seck_crops_2012]. Rice consumption has
increased globally over the last decade. Statista data shows that, in
the cropping year 2020/2021, the world population consumed about 504.3
million metric tons of rice, increasing from 437.18 million metric tons
in 2008/2009 [@cuaton_two_2022]. To meet the growing demand for rice and
ensure stable food supplies, efficient water management is essential.
However, irrigated rice farming requires significant water resources,
accounting for a substantial portion of global freshwater consumption
[@food__agriculture_organization_future_2018, @yang_water_2006]. As
water scarcity becomes an increasing concern, optimizing water use in
irrigated rice fields is crucial [@molden_improving_2010]**.**

Irrigated rice fields play a crucial role in Vietnam's agricultural
landscape, providing sustenance for its population and contributing
significantly to the national economy [@ngoc_benefits_2012]. However,
traditional manual leveling methods used in rice cultivation are
time-consuming, labor-intensive, and often result in uneven water
distribution, leading to sub-optimal crop growth and reduced yield
[@tuan_effects_2014]. To address these challenges, laser leveling
techniques have emerged as a promising solution for irrigated rice
fields. Here we enumerate some of the benefits of laser leveling, its
potential impact on agricultural productivity, and its suitability for
the Vietnamese context.

1.  Improved Water Management: Laser leveling technology ensures precise
    land grading, creating a uniform surface with minimal slope
    variations. This accuracy allows for efficient water management and
    enables uniform distribution across the rice fields
    [@nguyen_application_2019]. By achieving a consistent water depth,
    laser leveling reduces water wastage, enhances irrigation
    efficiency, and minimizes the risk of both water-logging and drought
    stress [@ngoc_benefits_2012].

2.  Increased Productivity and Yield: Uneven land surfaces can hinder
    crop growth, leading to uneven maturity and reduced overall yield.
    By providing a flat and consistent terrain, laser leveling promotes
    uniform plant growth, facilitates optimal nutrient absorption, and
    ensures a balanced distribution of sunlight [@tuan_effects_2014].
    These factors collectively contribute to increased crop productivity
    and improved rice grain quality.

3.  Cost and Labor Savings: Traditional manual leveling methods are
    labor-intensive and time-consuming. In contrast, laser leveling
    technology automates the land grading process, significantly
    reducing the need for manual labor [@nguyen_evaluating_2021]. This
    not only saves costs associated with hiring and managing labor but
    also expedites the cultivation process, allowing for timely crop
    rotations and potentially increasing the number of planting cycles
    per year [@hoang_benefits_2018].

4.  Environmental Sustainability: Laser leveling helps mitigate negative
    environmental impacts associated with traditional cultivation
    practices. By optimizing water distribution, it reduces water
    consumption and minimizes runoff, preserving this valuable resource
    [@ngoc_benefits_2012]. Additionally, by promoting uniform crop
    growth, it minimizes the need for excessive fertilizer and pesticide
    applications, thereby reducing chemical runoff and environmental
    pollution.

## Objective

The aim of this project is to determine whether laser leveling should be
applied by a small farmer rice cooperative in Vietnam or not.

# Methodology

Decision analysis is a systematic approach for making decisions under
uncertainty, incorporating mathematical and analytical techniques to
evaluate alternative courses of action and their potential outcomes. It
is a quantitative approach that aims to support decision-making
processes by explicitly considering uncertainties, trade-offs, and
potential consequences.

The decisionSupport package developed by @R-decisionSupport, provides a
systematic framework for making informed decisions based on a
combination of data, models, and stakeholder preferences. This R package
incorporates decision analysis techniques into a user-friendly software
tool, allowing decision-makers to analyze complex problems and evaluate
alternative courses of action. The methodology typically involves the
following steps:

1.  Problem Definition: Clearly defining the decision problem and
    identifying the objectives, constraints, and stakeholders involved.
    This step helps establish a clear understanding of the decision
    context.

2.  Data Collection: Gathering relevant data and information related to
    the decision problem. This may include historical data, expert
    opinions, stakeholder preferences, and other sources of information
    required for the analysis.

3.  Model Development: Developing mathematical or statistical models to
    represent the relationships between different variables and assess
    the potential outcomes of different decisions. The R package
    provides a range of modeling tools and techniques for decision
    analysis.

4.  Uncertainty Assessment: Quantifying uncertainties associated with
    key variables or parameters in the decision problem. This may
    involve statistical analysis, sensitivity analysis, or the use of
    probabilistic modeling approaches to estimate the range of possible
    outcomes.

5.  Decision Evaluation: Integrating the models, data and uncertainties
    to evaluate different decision alternatives. This involves comparing
    and ranking the alternatives based on multiple criteria, considering
    trade-offs and uncertainties.

6.  Sensitivity Analysis: Assessing the robustness of the decision
    results by examining the impact of changes in assumptions, input
    data, or models on the recommended decision.

7.  Communication and Implementation: Communicating the decision
    analysis results effectively to stakeholders and facilitating their
    understanding of the implications and trade-offs. This step helps in
    gaining consensus and support for the recommended decision and
    facilitating its implementation.

The decisionSupport R package provides a comprehensive set of functions
and tools to support decision analysis using the R programming language.
It offers a flexible and customizable platform for implementing decision
support methodologies, enabling users to perform sophisticated decision
analysis tasks efficiently.

## Decision Criteria

Because our main objective is to determine whether laser leveling could
be applied by a small farmer rice cooperative in Vietnam or not, first
we decided to focus on the economic and ecological criteria of laser
leveling, as recommended by [@oertle_potential_2019] since they
highlight the importance of introducing this not so well known topic so
far. They remark that is also important to demonstrate that this
technology could have an economic and environmental potential for
cooperative farmers. We know that we can implement this technology in
Vietnam because the government has implemented the "One Must do Five
Reductions" or 1M5R to promote sustainable rice production, which
includes laser leveling as a strategy. The following steps after this
project would be to hold a stakeholder dialogue to identify barriers and
drivers for future implementation.

For the model building process we determined first all the possible
variables for the economic and environmental components in our model and
design an input table, that is stored locally
as *Input_table_LL_decision.csv*, this table contains all the input
variables and their values used in the model.

Economical Criteria cost-effectiveness potential yield improvement
(fertilizer savings, yield increase, seed savings)

Ecological (Water use savings, GHGE, soil conservation)

## Package Management Section

Code for knitting bib 'project_packages.bib' was commented out to
prevent the code from overwriting the added references. The bib file
contains both the library packages and the references used for this
Rmarkdown file.

```{r package-installation, echo=TRUE}
# Install packages if needed (uncomment code):
# install.packages("decisionSupport")
# install.packages("dplyr")
# install.packages("ggplot2")
# install.packages("knitr")

library(decisionSupport)
library(dplyr)
library(ggplot2)
library(readr)
library(knitr)

#Automatically write R package citation entries to a .bib file
#knitr::write_bib(c(.packages(),
#                   'decisionSupport',
#                  'dplyr',
#                   'ggplot2'),'project_packages.bib')
```

## Conceptual model

![](figures/conceptual%20model.svg)

# Results

## Monte Carlo Simulation

Input table used is named *Input_table_LL_decision.csv* within this
Rproject folder. LL benefit ranges were lifted from Table 4 and 5 of
@nguyen-van-hung_precision_2022, divided by 5 since we consider yearly
values in this project, and not per 5-year period in contrast to the
cited literature. We consider 2 seasons per year since this is the
recommended assumption in the same literature, to maintain soil health
and prevent outbreak of rice diseases. We work with 1 hectare field size
for ease of comparison with literature later on.

```{r, echo=TRUE}
LL_model_function <- function(x, varnames){
  #browser() # enter the debugger 
  
  # calculate ex-ante risks ####
  intervention_No_coop_Event <- chance_event(chance_noLL, 1, 0, n = 1)
  # chance_event chooses with probability "intervention_No_coop_Event" the first scenario (1 in this case), otherwise 0 (no involvement)
  
  # precalculation of common random draws for all intervention model runs
  # benefits of rice cultivation WITH LL:        
    
  # Precalculationn for the change in yield with the intervention of Laser Leveling
  precalc_LL_yield <-
    vv(yield_LL, var_CV, n_years) * # yield [t/ha]
    vv(farm_area, var_CV, n_years) * # area of the field per farmer [ha]
    vv(rice_price, var_CV, n_years) # rice price [USD/t]
  
  # Precalculationn for the water savings with the intervention of Laser Leveling
  precalc_LL_water_savings <-
    vv(LL_water_saving, var_CV, n_years) * # water savings in [m^3/ha]
    vv(LL_water_cost, var_CV, n_years) * # cost of irrigation water [USD/m^3]
    vv(farm_area, var_CV, n_years) # area of the field per farmer [ha]
  
  # Precalculationn for the fertilizer savings with the intervention of Laser Leveling
  precalc_LL_fert_savings <-
    (vv(Fertilizer_cost_noLL, var_CV, n_years) - # fertilizer cost w/o LL [USD/ha]
    vv(Fertilizer_cost_LL, var_CV, n_years)) * # fertilizer cost with LL [USD/ha]
    vv(farm_area, var_CV, n_years) # area of the field per farmer [ha]
  
  # Precalculationn for the pesticide savings with the intervention of Laser Leveling
  precalc_LL_pest_savings <-
    (vv(Pesticide_cost_noLL, var_CV, n_years) - # pesticide cost w/o LL [USD/ha]
    vv(Pesticide_cost_LL, var_CV, n_years)) * # pesticide cost with LL [USD/ha]
    vv(farm_area, var_CV, n_years) # area of the field per farmer [ha]
  
  # Precalculationn for the seed savings with the intervention of Laser Leveling
  precalc_LL_seed_savings <-
    (vv(Seed_cost_noLL, var_CV, n_years) - # seed cost w/o LL [USD/ha]
    vv(Seed_cost_LL , var_CV, n_years)) * # seed cost with LL [USD/ha]
    vv(farm_area, var_CV, n_years) # area of the field per farmer [ha]
  
  # Precalculationn for the fuel savings with the intervention of Laser Leveling
  precalc_LL_fuel_savings <-
    (vv(Water_pumping_fuel_cost_noLL, var_CV, n_years) - # fuel w/o LL [USD/ha]
    vv(Water_pumping_fuel_cost_LL, var_CV, n_years)) * # fuel cost with LL [USD/ha]
    vv(farm_area, var_CV, n_years) # area of the field per farmer [ha]
  
  # Precalculationn for the labor cost savings with the intervention of Laser Leveling
  precalc_LL_labor_savings <-
    (vv(Labor_cost_noLL, var_CV, n_years) - # labor w/o LL [USD/ha]
    vv(Labor_cost_LL , var_CV, n_years)) * # labor cost with LL [USD/ha]
    vv(farm_area, var_CV, n_years) # area of the field per farmer [ha]
  
  # Precalculationn for the change in land use with the intervention of Laser Leveling
   precalc_LL_land_use <-
    vv(LL_land_USD_ha_year, var_CV, n_years) * # land savings LL [USD/ha]
    vv(farm_area, var_CV, n_years) # area of the field per farmer [ha]
  
  # summed benefits of rice production after LL:
  precalc_LL <-
    precalc_LL_yield + 
    precalc_LL_water_savings +
    precalc_LL_fert_savings + 
    precalc_LL_pest_savings + 
    precalc_LL_seed_savings +
    precalc_LL_labor_savings +
    precalc_LL_fuel_savings + 
    precalc_LL_land_use
    
    
    # benefits of rice cultivation WITHOUT LL:
  precalc_conv_prod <-
    vv(yield_noLL, var_CV, n_years) * # yield [t/ha]
    vv(farm_area, var_CV, n_years) * # area of the field per farmer [ha]
    vv(rice_price, var_CV, n_years) # rice price [USD/t]
  
  
  ####  Intervention Preamble ####
  
  # Run a simulation for both the application of LL and the conventional scenario without it:
  for (intervention_LL in c(FALSE,TRUE))
      {
  
  # Set the preambles for the case if LL application:    
  if (intervention_LL)
  {
    event_LL <- TRUE
    event_LL_cost <- TRUE
    event_LL_PlanningCost <- TRUE
    event_conv_rice_prod <- FALSE
  # Set the preambles for the normal rice production scenario
  } else
  {
    event_LL <- FALSE
    event_LL_cost <- FALSE
    event_LL_PlanningCost <- FALSE
    event_conv_rice_prod <- TRUE
  }
  
  if (intervention_No_coop_Event) {
    # only relevant if selected by chance and = TRUE
    # if this condition is TRUE the implementation of LL will be planned but not executed
    event_LL <- FALSE # no LL applied
    event_LL_cost <- FALSE # no establishment costs are created (planning costs however may occur)
    #event_LL_PlanningCost <- TRUE # the planning cost will still be applied since the project is aborted
    event_conv_rice_prod <- TRUE # the normal scenario takes place
}
    
  ####  Intervention ####
  
  # summing up the investment costs if LL is applied or not
  if (event_LL_cost) {
    investment_cost_LL <- establishment_cost_LL
  } else
    investment_cost_LL <- 0
  
  # calculating the planning costs ########MAYBE DONT USE########
  if (event_LL_PlanningCost) {
    plan_cost_intervention_LL <- planning_cost_LL + 
                                  zoning_cost_LL
  } else
    plan_cost_intervention_LL <- 0
  
  # calculating the maintenance costs, initializing the array with 0 costs for the first year:
  maintenance_cost <- rep(0, n_years) 
  
  # Cost of the application of LL per year 
  if (event_LL_cost)
    maintenance_cost <-
    maintenance_cost + 
    # add a variation of the variable over the years
    decisionSupport::vv(maintenance_cost_LL, var_CV, n_years)
  
  # First, all maintenance costs are stored in the variable:
  intervention_cost <- maintenance_cost
  
    # in the first year the establishment costs and planning costs are added:
  intervention_cost[1] <-
    intervention_cost[1] +  # equal to maintenance_cost [1]
    investment_cost_LL +    # equal to establishment costs
    plan_cost_intervention_LL
  
  
   #### Benefits from  cultivation in the intervention strips ####
  
  # Now all benefits of the intervention will be calculated
  # event_LL is 0 if the introduction of LL does not take place, thereby the gains would be multiplied by 0 = become 0
  
  # Benefits of intervention LL:
  intervention_LL_benefits <-
    as.numeric(event_LL) * precalc_LL
  
  # Benefits of conventional rice production (ground truth):
  no_LL_benefits <-
    as.numeric(event_conv_rice_prod) * precalc_conv_prod

  
  
  #### Total benefits from rice production ####
  
  # combined benefits (in reality: intervention_LL_benefits + 0 OR no_LL_benefits + 0)
  #rice_production <- intervention_LL_benefits + no_LL_benefits #not needed since we separate the cases in the next part
  
  
  # if the decision was to implement LL:
  if (intervention_LL){
    net_benefits <- intervention_LL_benefits - intervention_cost
    # save result in result_interv (result intervention):
    result_interv <- net_benefits
    # if the No Cooperation event takes place default to conventional production benefits 
    # but subtract intervention cost (which in this case will only contain planing costs)
    if (intervention_No_coop_Event){
    net_benefits <- no_LL_benefits - intervention_cost
    # save result in result_interv (result intervention):
    result_interv <- net_benefits}
  }

  
  # if the decision was to NOT implement LL:
  if (!intervention_LL){
    net_benefits <- no_LL_benefits - intervention_cost  
    # intervention-cost should be equal to planning costs (intervention_cost = planning costs IF no cooperation event takes place)
    
    # save result in result_n_interv (result NO intervention):
    result_no_interv <- net_benefits}
  
  
    } #close intervention loop bracket
  
  NPV_interv <-
  discount(result_interv, discount_rate, calculate_NPV = TRUE)

  NPV_no_interv <-
  discount(result_no_interv, discount_rate, calculate_NPV = TRUE)

# return all the data we want as output
return(list(LL_NPV = NPV_interv,
            NO_LL_NPV = NPV_no_interv,
            NPV_LL_added_value = NPV_interv - NPV_no_interv,
            Cashflow_LL_added_value = result_interv - result_no_interv))
}
```

Random seed is generated and will be stored throughout the simulation to
keep values and plots generated during project creation consistent with
future runs.

```{r monte-carlo-results, echo=TRUE}
# Generate a random seed
random_seed <- as.integer(Sys.time())  # Get the current time in seconds and convert it to an integer
# Set the random seed
set.seed(random_seed)
# Print the random seed
print(random_seed)


# Monte Carlo simulation results R code:
mcSimulation_results <- decisionSupport::mcSimulation(
  estimate = decisionSupport::estimate_read_csv("Input_table_LL_decision.csv", sep = ';', strip.white = TRUE),
  model_function = LL_model_function,
  numberOfModelRuns = 1e3, #run 10,000 times
  functionSyntax = "plainNames"
)

```

## Data Visualization

The simulated scenarios for the application of laser leveling visualized
using the `ggplot2` package [@R-ggplot2]. The code is shown below, as
well as the figures generated.

The density estimations of the NPV distribution plot of the Monte Carlo
Simulation model shows in yellow (LL_NPV) the expected NPV distribution
under the laser leveling intervention scenario, and in lila (NO_LL_NPV)
the scenario under conventional production practices (without the
intervention).

Because the 'do' LL_NPV scenario has a higher concentration of density
with a rightward trend in comparison with the NO_LL_NPV, it can be
concluded that the laser leveling intervention would have a higher
positive impact on the farmers economy, since the positive net present
value represents that the rate of return of the investment will be above
the discount rate. 

The boxplot of the distributions of the 'do' LL_NPV and 'do not do'
NO_LL_NPV decision scenarios illustrates the spread of the data in a
median (central line), with 25th and 75th percentiles. So here we can
see with a more detailed view, how the median NPV values differs between
scenarios, having the LL scenario a higher NPV than the business as
usual scenario. 

The introduction of laser leveling in rice production in Vietnam seems
to have a positive impact on the Net Present Value (NPV) over a time
span of 25 years.

Further, it can be seen that the 'do not do' NO_LL_NPV scenario has a
concentrated density range between 50,000 USD and 170,000 USD, while in
the 'do' LL_NPV scenario has a distribution between 60,000 USD and
185,000 USD - a right-hand-skew.

The maximum NPV with laser leveling LL_NPV is 245,320 USD, which is
higher compared to the maximum NPV without laser leveling NO_LL_NPV of
213,121 USD. Similarly, the minimum NPV for LL is 54,757 USD, while for
No LL, it is 53,758 USD. The mean NPV is 121,925 USD for LL and 107,581
USD for No LL. These statistics suggest that laser leveling can
potentially lead to improved economic returns in rice production.

The NPV of the added value NPV_LL_added_value that laser leveling
provides has a maximum value of 101,462 USD and a minimum value of
-62,091 USD. The mean NPV_LL_added_value is 14,343 USD. This indicates
that there can be instances where laser leveling may not provide
economic net benefits, as reflected by the negative minimum value.
However, on average, the NPV_LL_added_value is positive, implying a
positive impact of laser leveling on the added value in rice production.

The outcome distribution vs density estimation graph, displays the
estimated probability density of a variable along with the observed
distribution of outcomes, in our case this graph reflects the difference
between the NO_LL_NPV and LL_NPV scenarios, where the x-axis represents
the NPV while the y-axis represents the estimated probability density.
It can be seen that the curve is skewed to the right, which indicates
asymmetry and a higher distribution into the LL_NPV scenario, which
promotes laser leveling usage.

The cash flow over time plot, where the x-axis represents the duration
of the interventions, between 5 to 25 years in our case, while the
y-axis represents the magnitude of the cash flow, where positive values
indicate incoming cash flows (revenue, investments, etc.), and negative
values represent outgoing cash flows (expenses, payments, etc.). The
blue line in the 25-75% quantile is consistently positive and upward
sloping, which indicates a positive cash flow, where the mean cashflow
is 489 USD and cashflow per year with laser leveling
Cashflow_LL_added_value has a maximum value of 7,056 USD and a minimum
value of -6,206 USD. These statistics indicate that the costs and
benefits associated with laser leveling can vary across different
scenarios. However, the mean cashflow is positive, suggesting a
potential positive impact on the overall cashflow in rice production.

Overall, these specific values reinforce the notion that laser leveling
has the potential to enhance the economic viability and added value in
rice production in Vietnam. It is important to consider these specific
figures along with other factors such as cost-effectiveness,
environmental impact, and long-term sustainability when making decisions
about the implementation of laser leveling in agricultural practices.

```{r data visualization, echo=TRUE}
# Prevent display of digits in scientific notation for numbers up to 6 digits
options(scipen = 100, digits = 6)

# R code for vizualisation of results:

smooth_plt <- decisionSupport::plot_distributions(mcSimulation_object = mcSimulation_results, 
                                    vars = c("LL_NPV", "NO_LL_NPV"),
                                    method = 'smooth_simple_overlay',
                                    base_size = 16,
                                    colors = c("#FFC300", "#9f3ee2"),
                                    x_axis_name = "Outcome distribution [USD] NPV (N = 10,000)",
                                    y_axis_name = "Density of Estimations")

smooth_plt +
  scale_x_continuous(limits = c(-10000, 360000), breaks = seq(-100000, 300000, by = 100000)) +
  ggtitle ("Density of NPV Estimations") +
  #geom_hline(yintercept = median(c("LL_NPV", "NO_LL_NPV")), color="blue")
  geom_hline(yintercept = median(mcSimulation_results$LL_NPV), color = "red", linetype = "dashed")



hist_plt <- decisionSupport::plot_distributions(mcSimulation_object = mcSimulation_results, 
                                    vars = c("LL_NPV", "NO_LL_NPV"),
                                    method = 'hist_simple_overlay', 
                                    base_size = 16,
                                    colors = c("#FFC300", "#9f3ee2"),
                                    x_axis_name = "Outcome distribution [USD] NPV (N = 10,000)",
                                    y_axis_name = "Number of Outcomes in Bin")

hist_plt +
  scale_x_continuous(limits = c(-10000, 360000), breaks = seq(-100000, 300000, by = 100000))


NPV_names = c("Rice Production with Laser Leveling NPV", "Conventional Rice Production NPV")
decisionSupport::plot_distributions(mcSimulation_object = mcSimulation_results, 
                                    vars = c("LL_NPV", "NO_LL_NPV"),
                                    method = 'boxplot',
                                    new_names = "NPV_names",
                                    base_size = 16,
                                    colors = c("#FFC300", "#9f3ee2"),
                                    x_axis_name = "Outcome distribution [USD] NPV (N = 10,000)",
                                    y_axis_name = NULL)

decisionSupport::plot_distributions(mcSimulation_object = mcSimulation_results, 
                                    vars = "NPV_LL_added_value",
                                    method = 'boxplot_density',
                                    base_size = 16,
                                    colors = "#FFC300",
                                    x_axis_name = "Outcome distribution [USD] added value (N = 10,000)",
                                    y_axis_name = "Density of Estimations")



plot_cashflow(mcSimulation_object = mcSimulation_results, cashflow_var_name = "Cashflow_LL_added_value")



```

## Projection to Latent Structures (PLS) analysis

Application of post-hoc analysis to `mcSimulation()` outputs.

```{r, echo=TRUE}
library(decisionSupport)

#select the 3rd outcome variable "NPV_LL_added_value" from the mcSimulation results and run PLS simulation
pls_result <- plsr.mcSimulation(object = mcSimulation_results,
                  resultName = names(mcSimulation_results$y)[3], ncomp = 1)

input_table <- read.csv("Input_table_LL_decision.csv", sep = ";")
                        
plot_pls(pls_result, input_table = input_table, threshold = 0)

```

## Value of Information Analysis

Value of Information Analysis was conducted using EVPI.

The Variable Importance in the Projection (VIP) analysis derived by
statistically relating outputs to inputs using PLS regression, shows
colored horizontal bars, where blue represents a positive impact and red
a negative impact. This figure indicates which input variables had the
strongest influence on the model outputs, in our case the variables in
red were: the rice yield in conventional farming, the part of planing
cost, maintenance cost, land use savings and the price of the rice, this
variables. The further analysis of every variable will be needed to
understand its impact on NO_LL_NPV and  LL_NPV scenarios.

```{r, echo=TRUE}
#here we subset the outputs from the mcSimulation function (y) by selecting the correct variables
# this should be done by the user (be sure to run the multi_EVPI only on the variables that the user wants)
mcSimulation_table <- data.frame(mcSimulation_results$x, mcSimulation_results$y[1:3])

evpi <- multi_EVPI(mc = mcSimulation_table, first_out_var = "LL_NPV")
#> [1] "Processing 3 output variables. This can take some time."
#> [1] "Output variable 1 (LL_NPV) completed."
#> [1] "Output variable 2 (NO_LL_NPV) completed."
#> [1] "Output variable 3 (NPV_LL_added_value) completed."

plot_evpi(evpi, decision_vars = "LL_NPV")
#> Warning: There are no variables with a positive EVPI. You probably do not need a
#> plot for that.
#> 
compound_figure(mcSimulation_object = mcSimulation_results, input_table = input_table, plsrResults = pls_result, EVPIresults = evpi, decision_var_name = "NPV_LL_added_value", cashflow_var_name = "Cashflow_LL_added_value", base_size = 7)

```

# Discussion

According to @galindo-prieto_variable_2014, VIP values greater than 1
point are the most relevant variables, while VIP values below 0.5 are
considered irrelevant. According to our results in the VIP graph, rice
yield is the variable with more positive and negative impact with a
higher value than 1 in the blue and red bars. After multiple runs with
different values, we found that rice yield with and without LL are the
variables worth investing to research more on to make more informed
decision in our context. Farm size was not a VIP in our runs, as was the
VIP plot results showed by @sapkal_impact_2019emphatized, where they
highlight that LL is a scale-neutral technology and is not biased
towards farmers who own huge chunks of land.

By leveling rice fields, 20 - 40 % of water can be saved, and at the
same time, weed can be reduced by 40% due to more consistent water
coverage, which results in less pesticide use and excessive working
hours [@van_nguyen_reporting_2019].

Consideration should be given to the scalability and replicability of
the application of laser leveling in Vietnam. According to
@nguyen-van-hung_precision_2022**,** the cost savings obtained from LLL
application were in the range of USD 1110--1331 ha−1 5 years−1, around
222 - 266.2 ha−1 yr; these values are consistent with our cash flow
analysis, where median value (blue line) in the 25-75% quantile goes
around 489 USD. This indicates that the potential for scaling up the
implementation of laser leveling technology across different regions and
farming systems is promising. Also, this introduces the implications
that policies at the national or regional level, that promotion of laser
leveling technology, would be valuable. Creating a holistic picture and
understanding the broader economic, social, and environmental impacts,
as well as the necessary policy framework can guide the integration of
laser leveling into agricultural development plans and strategies.

For this vision to work, exploring the challenges and barriers is
essential to the widespread adoption of laser leveling in Vietnam. This
could involve assessing the availability and accessibility of laser
leveling equipment, training and technical support for farmers. As it
stands, there is only a limited amount of companies that provide laser
leveling services, but the numbers are constantly increasing
[@van_nguyen_reporting_2019].

In addition to policy incentives, financial support from foreign or
private sources to encourage the adoption of this technology in Vietnam
may benefit locals, investors and the environment likewise. Identifying
potential challenges early on was always what enables stakeholders to
develop strategies to overcome them and ensure successful implementation
at a larger scale. This may be what separates bad from great investors.

## Decision recommendation

Overall, the results generated highlight that the adoption of LL is more
preferable in the context of smallholder cooperative in Vietnam compared
to non-adoption in terms of the costs and benefits taken into account in
this study.

# Conclusion

In conclusion, the Monte Carlo simulation analysis of laser leveling
intervention in rice production in Vietnam has demonstrated the
potential economic benefits and positive impact of this technology. The
results indicate that laser leveling has the potential to enhance the
economic viability and NPV in rice production.

While there can be instances where laser leveling may not provide
economic net benefits, on average, it contributes positively to the
added value and we showed that that laser leveling has the potential to
generate improved economic returns and higher NPV in rice production
over a 25-year timeframe for each hectare leveled.

Additionally, we conducted an analysis of cash flow over time that also
indicated a positive impact of laser leveling on the overall cash flow
in rice production, thereby showing how the investments starts to pay
off from the first year consistently, further supporting the potential
economic benefits associated with laser leveling.

Through the Variable Importance in the Projection analysis, several
variables have been identified as more or less important. These findings
should be carefully considered and analyzed in future studies and
decision-making processes.

Furthermore, apart from the economical perspective there is also an
ecological perspective which should not be completely neglected as laser
leveling comes with beneficial and sustainable characteristics, namely
reduced greenhouse gas emissions and erosion, less need for
agrochemicals such as fertilizer and pesticides, as well as increased
freshwater water savings.

However, we also addressed challenges and barriers to widespread
adoption of laser leveling, including how to ensure the accessibility of
laser leveling equipment, providing training and technical support.
Moreover, we noted that it is important to raise awareness for this
technology as the consideration of policy incentives and financial
support to promote it is necessary to implement laser leveling at a
larger scale.

In conclusion, the results from this modelling highlight the potential
benefits of laser leveling in rice production, creating a basis of
insights for decision-makers, especially small-scale farmers and farmer
cooperations, to work with. Our findings underline the importance of
even more comprehensive research of the impact of laser leveling,
financial and political support, as well as holistic thinking to fully
explore the potential of laser leveling in economically sustainable
Vietnamese rice production.

# References
