---
title: "Decision Analysis for Laser Leveling Application"
subtitle: "Creating a decision support model for smale scale farmers in Vietnam using the decisionSupport R package by Lüdeling et al."
author: "Marina, Sara, Kent, Frederic, Grace"
output: pdf_document
date: "`r Sys.Date()`"
bibliography: project_packages.bib
---

---

# Introduction

## Background
-Overview
-potential benefits
-relevance of the decision for farmers


## Objective
-Determine whether laser leveling should be applied by a small farmer in Vietnam

# Methodology
-Methods we use
-Decision analysis theory

## Decision Criteria (maybe with Data Sources?)
-features of our input table explained and sorted by overlying category (eg. Economical, Ecological etc.)

**Economical Criteria**
cost-effectiveness
potential yield improvement

**Ecological Criteria**
environmental impact

**Social Criteria**
ease of implementation


## Package Management Section

```{r package-installation, echo=TRUE}
# Install packages if needed (uncomment code):
# install.packages("decisionSupport")
# install.packages("dplyr")
# install.packages("ggplot2")

library(decisionSupport)
library(dplyr)
library(ggplot2)
```

```{r, warning=FALSE, include = FALSE}
#Automatically write R package citation entries to a .bib file
knitr::write_bib(c(.packages(),
                   'decisionSupport',
                   'dplyr',
                   'ggplot2'),'project_packages.bib')
```

# Data Preparation

## Loading and organizing existing data and assumptions made

```{r data preparation, echo=TRUE}
# data loading and sorting R code:

```

# Analysis

## Cost Analysis
Performing a cost analysis comparing the expenses associated with laser leveling to the potential benefits it may bring.

```{r cost-analysis, echo=TRUE}
# cost analysis R code:

```

## Yield Analysis
Performing an analysis to determine the potential yield improvement laser leveling could offer in comparison to tradtional farming. 

```{r yield-analysis, echo=TRUE}
# yield analysis R:

```

## Sensitivity Analysis
Conducting a sensitivity analysis to assess the impact of varying key parameters and assumptions on the decision outcome.
Maybe explore different scenarios and evaluate their influence on the decision to adopt laser leveling?

```{r sensitivity-analysis, echo=TRUE}
# sensitivity analysis R code:

```

# Results

## Monte Carlo Simulation Results
Include:
-probability distributions
-sensitivity analyses
-relevant metrics or charts that provide insights into the decision-making process

```{r monte-carlo-results, echo=TRUE}
# Monte Carlo simulation results R code:

```

## Data Visualization
The simulated scenarios for the application of laser leveling visualized using the `ggplot2` package [@R-ggplot2]
-Time charts?

```{r data visualization, echo=TRUE}
# R code for vizualisation of results:

```



## Decision Recommendation
-based on the analysis and simulation results of whether or not to implement laser leveling
considering:
-decision criteria
-cost-benefit analysispotential risks and uncertainties.

# Conclusion

-summary of the key findings 
-implications of the recommendation 
-areas for future research or consideration

